Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Privacy @naszam

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs and homomorphic encryption (see § Privacy in 3.2).

>>>>

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).
